---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dtheory

<!-- badges: start -->
<!-- badges: end -->

The goal of dtheory is to provide a more practical and useful set of functions for carrying out d-studies from Generalizability Theory, specifically for studies with a random p x t design.

## Installation

You can install the development version of dtheory from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tclark23/dtheory")
```

## Usage

Imagine you had this simple data frame from a small study you did, and you wanted to find the optimal number of trials for future studies. Using Generalizability Theory, the dstudy() function calculates G-coefficients for each specified number of trials, so that you can determine the minimum number which would provide an adequate reliability coefficient (typically 0.8 is set as the threshold).

```{r example}
library(dtheory)
x <- data.frame(c(1,1,1,2,2,2,3,3,3), c(1,2,3,1,2,3,1,2,3), c(12, 14, 12, 22, 22, 19, 17, 22, 20))
colnames(x) <- c("Person", "Trial", "Metric")
dstudy(x, col.scores = "Metric", from = 1, to = 10, by = 1)
```
Just like magic!

Or, say you have already decided on the number of trials you wish to use. Continuing from the previous example, let's use n = 2. But now, you want to find the confidence interval for that G-coefficient at the alpha = .05 confidence level. For that, we can use the ```dconf``` function!
```{r}
dconf(x, col.scores = "Metric", n = 2)
```
NOTE: The ```dconf()``` confidence interval calculation, originally developed by Arteaga et al. (1982) assumes that score effects are normally distributed. Hence, any attempt to use ```dconf()```with non-normal data will not produce a reasonable result!
